Title Goes Here

### 2020-04-17 analysis/paper/paper.Rmd
add more plots

```{r}
library(ggbiplot)

@@

#group them by three phase
library(ggfortify)

@@

# phase 3
xx_pca3 <- 
df_sitename %>% 
  filter(SPstage.Stage != 2) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

xx_pca1_3 <- 
  data.frame(xx_pca3$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage !=2]))

@@

xx_pca2 <- 
df_sitename %>% 
  filter(SPstage.Stage != 3) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

xx_pca1_2 <- 
  data.frame(xx_pca2$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage !=3]))

ggplot(xx_pca1_2 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()
```

@@

# artifacts from SYG6 site
SYG6_files <- dir(datadir, pattern = "SYG6_*")

ML = c()
BL = c()
TL = c()
SL = c()
MW = c()
TW = c()
SW = c()
for (i in 1:length(SYG6_files)) {
  filename <- paste(datadir, SYG6_files[i], sep = "")
  print(filename)
  landmarks <- read.tps(filename)
  ML <- c(ML, landmark_dist(landmarks, 1, 7))
  BL <- c(BL, bl_dist(landmarks))
  TL <- c(TL, tl_dist(landmarks))
  SL <- c(SL, sl_dist(landmarks))
  MW <- c(MW, landmark_dist(landmarks, 2, 11))
  TW <- c(TW, landmark_dist(landmarks, 3, 10))
  SW <- c(SW, landmark_dist(landmarks, 5, 8))
}

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files)
#list of all attributes without ID
DF <- df[,1:7]

#simpler way to calculate Correlataion, you can use
cor(DF)

#simpler way to calculate Correlataion, you can use
cor(DF)

# CV%
sd(ML)/mean(ML)*100
sd(BL)/mean(BL)*100
sd(TL)/mean(TL)*100
sd(SL)/mean(SL)*100
sd(MW)/mean(MW)*100
sd(TW)/mean(TW)*100
sd(SW)/mean(SW)*100

#CV ranges are 20-33% more broad...
```

>>>>

```{r}
library(ggbiplot)
library(ggfortify)

@@

@@

xx_pca2 <- 
df_sitename %>% 
  filter(SPstage.Stage == 2) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

xx_pca1_2 <- 
  data.frame(xx_pca2$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage ==2]))

ggplot(xx_pca1_2 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

# phase 3

xx_pca3 <- 
df_sitename %>% 
  filter(SPstage.Stage == 3) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

xx_pca1_3 <- 
  data.frame(xx_pca3$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage ==3]))

@@

@@

# artifacts from SYG6 site
library(stringr)
SYG6_df <- 
  df %>% 
  filter(str_detect(files, "SYG6"))

SYG6_df_sitename <- SYG6_df %>% 
  mutate (files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

#list of all attributes without ID
SYG6_DF <- SYG6_df[,1:7]

#simpler way to calculate Correlataion, you can use
cor(SYG6_DF)

#a scatterplot matrix of Correlation
pairs(SYG6_DF)

# CV
map_df(SYG6_DF, cv)

SYG6_PCA <- prcomp(SYG6_DF, center = TRUE, scale = TRUE)

# remove stage 1 artefact
SYG6_xx_pca <- 
SYG6_df_sitename %>% 
  filter(SPstage.Stage != 1) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

SYG6_xx_pca1 <- 
  data.frame(SYG6_xx_pca$x,
             stage = as.factor( SYG6_df_sitename$SPstage.Stage[SYG6_df_sitename$SPstage.Stage !=1]))

#plot for both stage
SYG6_gg_stage <- 
ggplot(SYG6_xx_pca1 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()
